\documentclass{beamer}
\usetheme{Boadilla}
\title[Cloud Computing]{Cloud Computing \& OpenStack}
\subtitle[Overview]{An Overview}
\author[EternalTyro]{EternalTyro}
\institute[A]{
      Dummy Company\\
      Dummy workshop\\[1ex]
      \texttt{http://dummydummy.com}
}
\date{June, 22 2013}
\begin{document}

%--- the titlepage frame -------------------------%
\begin{frame}[plain]
  \titlepage
\end{frame}

%--- the presentation begins here ----------------%
\begin{frame}{Cloud computing}

\begin{definition}
 ..computing resources provided over the Internet as services on demand via API calls..
\end{definition}
\pause

\begin{itemize}
 \item Computing resources
 \pause
 \item over the Internet (or network)
 \pause
 \item anything as a Service (*aaS)
 \pause
 \item service on demand
 \pause
 \item API access
\end{itemize}
\end{frame}

\begin{frame}{Advantages of cloud}
Advantages:
\begin{itemize}
 \item Highly reliable and robust
 \pause
 \item Highly available
 \pause
 \item Heterogenous
 \pause
 \item Highly scalable
 \pause
 \item Highly manageable
 \pause
 \item Performance \& Speed
 \pause
 \item Metered \& on demand
\end{itemize}
\end{frame}


\begin{frame}{Available Cloud Platforms}
Popular public cloud platforms: Internet based; little control on data and infrastructure.
\begin{itemize}
 \item Amazon Web Services (AWS)
 \item Rackspace Cloud
 \item Domestic players like Sify, ISPs, etc.
\end{itemize}
\pause
Popular private cloud platforms: On premise.
\begin{itemize}
 \item Eucalyptus
 \item OpenStack
\end{itemize}
\pause
Public and private clouds may be mixed and used in a hybrid cloud model.
\end{frame}

\begin{frame}{OpenStack}
\begin{itemize}
 \item Cloud framework
 \item Founded by NASA \& Rackspace
 \item Compute \& Storage in the beginning
 \item Written in Python
 \item REST based APIs
 \item Apache Licensed
\end{itemize}
\end{frame}

\begin{frame}{Components}
\begin{itemize}
 \item Nova
 \pause 
 \item Glance
 \pause
 \item Cinder
 \pause
 \item Quantum
 \pause
 \item Swift
 \pause
 \item Keystone
 \pause
 \item Ceilometer
 \pause
 \item Horizon
\end{itemize}
\end{frame}

\begin{frame}{Nova Compute}
\begin{itemize}
 \item Manages VMs aka instances and their lifecycle
 \item LXC, KVM, Xen, etc.
 \item ARM / x86 / AMD64
 \item Host - Guest isolation; Guest - Guest isolation
\end{itemize}
\end{frame}

\begin{frame}{Features}
\begin{itemize}
 \item Support for commodity servers
 \item Networking support - Flat / DHCP / VLAN / IPv6
 \item REST-ified API
 \item Floating IPs
 \item RBAC
\end{itemize}
\end{frame}

\begin{frame}{Glance}
\begin{itemize}
 \item Image delivery service
 \item Snapshots
 \item RAW, QCOW, VMDK, VDI, AMI etc.
\end{itemize}
\end{frame}

\begin{frame}{Cinder}
\begin{itemize}
 \item Block storage service
 \item Analogous to EBS
 \item Persistant, Mountable
\end{itemize}
\end{frame}

\begin{frame}{Quantum}
\begin{itemize}
 \item Manages networking for instances
 \item Network connectivity as a Service
 \item Pluggable, Scalable
 \item API driven
 \item Extension framework: IDS / Firewalls / LB / VPN
\end{itemize}
\end{frame}

\begin{frame}{Nova Swift}
\begin{itemize}
 \item Object Storage
 \item Analogous to S3
 \item REST API, duh..
 \item Hash rings
\end{itemize}
\end{frame}

\begin{frame}{Keystone}
\begin{itemize}
 \item Identity and access management
 \item Password, token and key based access mechanisms
 \item LDAP? oh yes!
 \item Service lists
 \item RBAC
 \item ...and APIs
\end{itemize}
\end{frame}

\begin{frame}{Other components}
\begin{itemize}
 \item Schedulers
 \item Queue
 \item Metering
 \item Monitoring \& Management.
\end{itemize}
\end{frame}

\begin{frame}{Control Flow}
\begin{itemize}
 \item User initiates an Instance from within the Dashboard
 \item Authentication \& authorization token from Keystone
 \item Token and Catalog sent through the AMQP to the Scheduler
\end{itemize}
\end{frame}

\begin{frame}{Be a hero}
\begin{itemize}
 \item Code
 \item Build, deploy and document
 \item File bugs
 \item ..or fix bugs
 \item Document, blog and share
\end{itemize}
\end{frame}

\begin{frame}{Get Help}
\begin{itemize}
 \item IRC \#openstack on freenode
 \item Official documentation docs.openstack.org
 \item Blogs, wikis, etc..
 \item Meetups
\end{itemize}
\end{frame}

\begin{frame}{Thank You!}
\begin{center}
Questions??
\end{center}
\end{frame}

\end{document}
